Baseline centering problem

### 2018-12-12 paper/tangotd.tex

This contains: Section~\ref{sec:tdconv}: remarks on recovering the known convergence results
for TD in a single framework, plus ideas on systematic variants around
two-timescale algorithms or improved ``almost-one-timescale'' algorithms.

@@

>>>>

These notes contain: Section~\ref{sec:tdconv}: remarks on recovering the known convergence results
for TD in a single framework, plus ideas on systematic variants around
two-timescale algorithms or improved ``almost-one-timescale'' algorithms.

@@

The fixed point $\hat V_1$ for variant 1 has less clear an
interpretation. Defining the matrix $\eps$ via $\Delta \eqd(\Id+\eps\rho)\tilde \Delta$ where
$\eps$ is some hopefully small model error, we find
\begin{align}
\hat V_2&=C^{-1}\transp{(\rho\tilde \Delta)}R
\\&=\left(
\Delta+\frac{(\transp{(\rho\tilde \Delta)})^{-1}\transp{\Delta} \rho \tilde
\Delta-\Delta}{2}
\right)^{-1}R
\\&=\left(
\Delta+\frac12(\transp{\eps}-\eps)\rho\tilde \Delta
\right)^{-1}R
\end{align}
In particular, if $\eps$ is symmetric the error vanishes, but if $\eps$
is antisymmetric we end up computing $\tilde \Delta^{-1}R$, namely the
Bellman function of the model. Usually $\eps$ would be somewhere in
between; I do not know if it is possible to force the model to favor
symmetric values of $\eps$.

In view of this, variant 2 seems more promising, although it relies on
rewards depending only on $s$ or only on $s'$, not on the pair $(s,s')$.
